---
title: 'Text mining, sentiment analysis, and visualization'
date: 'created on 22 november 2020 and updated `r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---
```markdown
_Last updated:_ `r Sys.time()`

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)
library(here)

# For text mining:

library(pdftools)
library(tidytext)
library(textdata) 
library(ggwordcloud)
```

### Getting the Game of Thrones book as readable data:
```{r get-document}
got_path <- here("data","got.pdf")
got_text <- pdf_text(got_path)
```

Example: Just want to get text from a single page (e.g. Page 9)? 
```{r single-page}
got_p9 <- got_text[9]
got_p9
```


```{r split-lines}
got_df <- data.frame(got_text) %>% 
  mutate(text_full = str_split(got_text, pattern = '\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full)) 
```

```{r tokenize}
got_tokens <- got_df %>% 
  unnest_tokens(word, text_full)

```

```{r count-words}
got_wc <- got_tokens %>% 
  count(word) %>% 
  arrange(-n)
got_wc
```


### Removing stop words:
```{r stopwords}
got_stop <- got_tokens %>% 
  anti_join(stop_words) %>% 
  select(-got_text)
```

#Checking the counts again: 
```{r count-words2}
got_swc <- got_stop %>% 
  count(word) %>% 
  arrange(-n)
```

```{r skip-numbers}
got_no_numeric <- got_stop %>% 
  filter(is.na(as.numeric(word)))
```

### Word cloud 

```{r wordcloud-prep}
# There are almost 2000 unique words 
length(unique(got_no_numeric$word))

# We probably don't want to include them all in a word cloud. Let's filter to only include the top 100 most frequent?
got_top100 <- got_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)
got_top100
```

```{r wordcloud}
got_cloud <- ggplot(data = got_top100, aes(label = word)) +
  geom_text_wordcloud() +
  theme_minimal()

got_cloud
```

# customizing:
```{r wordcloud-pro}
ggplot(data = got_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n), shape = "circle") +
  scale_size_area(max_size = 24) +
  scale_color_gradientn(colors = c("darkgreen","blue","red")) +
  theme_minimal()
  
```


"afinn": Words ranked from -5 (very negative) to +5 (very positive)
```{r afinn}
get_sentiments(lexicon = "afinn")

afinn_pos <- get_sentiments("afinn") %>% 
  filter(value %in% c(3,4,5))

afinn_pos
```

bing: binary, "positive" or "negative"
```{r bing}
get_sentiments(lexicon = "bing")

```


```{r nrc}
get_sentiments(lexicon = "nrc")

```


### Sentiment analysis with afinn: 

```{r bind-afinn}
got_afinn <- got_stop %>% 
  inner_join(get_sentiments("afinn"))
got_afinn
```

```{r count-afinn}
got_afinn_hist <- got_afinn %>% 
  count(value)

# Plotting them: 
ggplot(data = got_afinn_hist, aes(x = value, y = n)) +
  geom_col(aes(fill = value)) +
  theme_bw()
```

```{r afinn-2}
# What are these '2' words?
got_afinn2 <- got_afinn %>% 
  filter(value == 2)
```

```{r afinn-2-more}
# Checking the unique 2-score words:
unique(got_afinn2$word)

# Counting & plotting them
got_afinn2_n <- got_afinn2 %>% 
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(factor(word), n))


ggplot(data = got_afinn2_n, aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  theme_bw()

```

#Summarizing the Game of Thrones 
```{r summarize-afinn}
got_summary <- got_afinn %>% 
  summarize(
    mean_score = mean(value),
    median_score = median(value)
  )
got_summary
#With the median score of the sentiment analysis of Game of Thrones being -1
```



```{r bind-bing}
got_nrc <- got_stop %>% 
  inner_join(get_sentiments("nrc"))
```


```{r check-exclusions}
got_exclude <- got_stop %>% 
  anti_join(get_sentiments("nrc"))

# View(got_exclude)

# Count to find the most excluded:
got_exclude_n <- got_exclude %>% 
  count(word, sort = TRUE)

head(got_exclude_n)
```


Counts: 
```{r count-bing}
got_nrc_n <- got_nrc %>% 
  count(sentiment, sort = TRUE)

# Plotting:

ggplot(data = got_nrc_n, aes(x = sentiment, y = n)) +
  geom_col(aes(fill = sentiment))+
  theme_bw()
  
ggsave("sentiment_plot_got.png")
```

Counting by sentiment *and* word, then facet:
```{r count-nrc}
got_nrc_n5 <- got_nrc %>% 
  count(word,sentiment, sort = TRUE) %>% 
  group_by(sentiment) %>% 
  top_n(5) %>% 
  ungroup()

got_nrc_gg <- ggplot(data = got_nrc_n5, aes(x = reorder(word,n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, ncol = 2, scales = "free") +
  coord_flip() +
  theme_minimal() +
  labs(x = "Word", y = "count")

# Show it
got_nrc_gg

# Save it
ggsave(plot = got_nrc_gg, 
       here("figures","got_nrc_sentiment.png"), 
       height = 8, 
       width = 5)
```

